An Analysis of The Characteristics of the Top Private Equity Firms in the United States That Determine ESG Practices.

### 2024-04-19 paper/paper.qmd
Final Edits

The corporate landscape is rapidly evolving, with a notable shift towards greater responsibility and transparency, spurred by the rise of Environmental, Social, and Governance (ESG) considerations. While ESG has gained traction in publicly traded companies, there is a significant gap in understanding the ESG practices of private equity (PE) firms, despite their immense global impact. This gap is particularly surprising given the influential role PE firms play in the economy and their potential impact on ESG. This paper aims to address this gap by investigating the determinants and practices of ESG within PE firms.

This paper aims to reproduce the Top 100 US Private Equity Firms paper. That paper focuses on the top 100 PE firms based in the United States, conducting a thorough analysis of their ESG practices through content analysis of their websites. The findings reveal a notable lack of comprehensive ESG disclosures among PE firms, with only a minority providing substantial information on their environmental, social, and governance initiatives. This paper aims to improve upon their work by firstly amending the data collected for certain variables, such as number of employees. Next, this paper calculates next metrics, such as average fund size. Lastly, the paper focuses on different predictor variable. The reasons for each improvement is detailed in the paper.

@@

This paper is structured as follows. In Section 2, the source of the data, the methodology of data collection and cleaning, and the changes made to the data set is detailed. Section 3 discusses the choice and construction of our logistic model to make predictions about private equity firms. Section 4 presents the model's results. Section 5 draws upon the relevance of these results to Europe. Section 6 talks about the implications, ethical considerations, and limitations of our work.

@@

# Model

@@

# Results

@@

# Discussion

>>>>

The corporate landscape is rapidly evolving, with a notable shift towards greater responsibility and transparency, spurred by the rise of Environmental, Social, and Governance (ESG) considerations. Whilst ESG has gained traction in publicly traded companies, there is a significant gap in understanding the ESG practices of private equity (PE) firms, despite their immense global impact. This gap is particularly surprising given the influential role PE firms play in the economy and their potential impact on ESG. This paper aims to address this gap by investigating the determinants and practices of ESG within PE firms.

This paper aims to reproduce the ESG in Top 100 US Private Equity Firms paper, and uses the dataset that were constructed by its authors [@paper]. That paper focuses on the top 100 PE firms based in the United States, conducting a thorough analysis of their ESG practices through content analysis of their websites. This paper aims to build upon their work by firstly amending the data collected for certain variables, such as number of employees. Secondly, this paper calculates new metrics, such as average fund size. Thirdly, a new methodology is used to calculate a firm's ESG score. Lastly, the paper focuses on different predictor variables. The reasons for each modification is detailed in the paper.

@@

This paper is structured as follows. In @sec-data, the source of the data, the methodology of data collection and cleaning, and the changes made to the data set is detailed. @sec-model discusses the choice and construction of our negative model. @sec-results presents the model's results. @sec-discussion further discusses the results, comparing it to the original paper, and discusses the limitations of the paper

@@

# Model {#sec-model}

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
